---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  font-family: 'Helvetica', sans-serif;
  line-height: 1.6;
  color: #333;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 5px;
}
.bold-highlight {
  font-weight: bold;
  color: #e74c3c;
}
```

## Analyzed My Youtube Viewing Habits

This report analyzes my YouTube viewing data, summarizing video durations and content categories. It also provides visual insights into the types of videos I watch.

### Summary of Video Durations

The dataset includes a collection of YouTube videos I've watched. Below are some key statistics about the videos I watched:

```{r}
#load the dataset
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSrX2I61AkPoUlCu2wAf3B9dHucB0_RgBPiJ7LfXcImY1YU1oXKoAS8v-_WIoUN2qV4OdiyOFsKFdHI/pub?output=csv")

#rename variables and create a new data frame
latest_data <- logged_data %>%
  rename(
    date_watched = `When did you watch these videos?`,
    video_title = `What is the title of the YouTube video?`,
    video_category = `Which category best describes the content of the video?`,
    video_duration = `How long is the video? (in minutes)`,
    enjoyment_rating = `Enjoyment rating`,
    recommend_video = `Would you recommend this video to others?`
  )

#calculate the average and max video duration
summary_values <- latest_data %>%
  summarise(
    avg_duration = mean(video_duration, na.rm = TRUE),
    max_duration = max(video_duration, na.rm = TRUE)
  )
avg_duration <- summary_values$avg_duration
max_duration <- summary_values$max_duration
```

On average, I spend `r round(avg_duration, 1)` minutes watching a YouTube videos, and the longest video I watched was `r max_duration` minutes.

### Video Distribution

The bar chart below shows how my watched videos are distributed across different categories and the length of videos I typically watch:

```{r}
ggplot(latest_data, aes(x = video_category)) +
  geom_bar(fill = "maroon") +
  labs(title = "Distribution of Video Categories", x = "Video Category", y = "Count") +
  theme_minimal() +
  coord_flip()
```

```{r}
latest_data <- latest_data %>%
  mutate(duration_group = case_when(
    video_duration < 10 ~ "<10 minutes",
    video_duration >= 10 & video_duration <= 60 ~ "10-60 minutes",
    video_duration > 60 ~ ">60 minutes"
  ))

#plot the bar chart with the duration categories
ggplot(latest_data, aes(x = factor(duration_group,
                                   levels = c("<10 minutes", "10-60 minutes", ">60 minutes")))) +
  geom_bar(fill = "#3F6D9B", color = "black") +
  labs(title = "Distribution of Video Duration", x = "Video Duration", y = "Count") +
  theme_minimal()
```

### Conclusion

From this analysis, I can see that the majority of my videos fall into the education category, reflecting a strong interest in learning and gaining knowledge. Additionally, most of the videos I watch are between `r duration_group[which.max(table(duration_group))]` long, indicating that I prefer content of a moderate length.
